Review: The Extent of Adaptive Wild Introgression in Crops

### 2018-07-06 paper.tex

\end{document}

>>>>

\end{document}
=======
\documentclass[11pt]{article}
\usepackage{color}
\usepackage{authblk}%allows footnote format for authors
\usepackage[letterpaper, margin=1in]{geometry} %package that allows changes in margins and header/footers
\usepackage[numbers,sort]{natbib}
\usepackage{amsmath}
\usepackage{rotating}
\usepackage{adjustbox}
\usepackage[english]{babel}
\usepackage{colortbl}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage[x11names,dvipsnames,table]{xcolor}
\usepackage{array}
\newcolumntype{G}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\bibliographystyle{ieeetr}
\newcommand{\mbh}[1]{\textcolor{orange}{ \emph{\scriptsize  #1}} } %creating command for Matt's comments
\newcommand{\lwang}[1]{\textcolor{red}{ \emph{\scriptsize  #1}} } %creating command for Li's comments
\newcommand{\gmj}[1]{\textcolor{blue}{ \emph{\scriptsize  #1}} } %creating command for Garrett's comments

\author[1]{Authors: Garrett M. Janzen}%author information
\author[1]{Li Wang}
\author[1,*]{Matthew B. Hufford}
\affil[1]{Department of Ecology, Evolution, and Organismal Biology, Iowa State University, Ames, Iowa, USA}
\affil[*]{Correspondence: mhufford@iastate.edu (M.B. Hufford)}
\date{}

Plant domestication is often conceptualized as a geographically constrained process, with crops originating from a wild progenitor within one or more defined centers followed by expansion to the modern-day range of cultivation \cite{Harlan1992}.
However, archaeological and genetic evidence are beginning to reveal that, in many cases, domestication has been temporally protracted and geographically diffuse \cite{Meyer2016, Wang2017, Fuller2014}.
An additional important aspect of the emerging complexity of domestication is the occurrence of beneficial gene flow from locally adapted wild relatives to crops during their expansion following domestication.
It is this adaptive introgression that is the subject of this review.

Adaptive introgression has three components: hybridization between differentiated taxa, backcrossing to one of the parents, and selection on recombinant genotypes with progressively diminished linkage drag \cite{barton2001role}.
In domesticated species, adaptive introgression would consist of crop-wild hybrids backcrossing to a crop followed by increase in frequency of adaptive wild alleles in the crop and selection against undesirable wild background.
To date, the literature on crop-wild gene flow has largely focused on the risk of transgene introgression from domesticated crops into wild relatives (for a review, \cite{stewart2003transgene}) and on modern plant breeding efforts to introgress desired traits from wild relatives (for a review, \cite{Dempewolf2017}).
The history of natural and potentially adaptive introgression of wild alleles into domesticated crops over evolutionary timescales has received considerably less attention.
Recently developed tools and methods have been applied to high-density marker data to detect genome-wide patterns of introgression, granting novel insight into the prevalence of adaptive introgression in crop histories.
Results from these studies suggest there is a need to expand our conception of domestication to encompass the broadening of the genetic base of crops that occurred through adaptive gene flow from newly encountered wild relatives during post-domestication expansion.

In this review, we: 1) briefly describe recently developed methods for detecting introgression, 2) present case studies suggesting wild-to-crop introgression has conferred local adaptation, 3) consider how introgression bears upon fundamental questions of domestication, and 4) describe key questions regarding crop adaptation through gene flow from wild relatives.

The decreasing cost of genome-wide resequencing and availability of reduced-representation genotyping (\emph{e.g.}, GBS and RAD-Seq), combined with new analytical methods (\textbf{Table 1}), has facilitated the comprehensive study of introgression across a broad spectrum of species.
The methods reviewed here do not include those estimating introgression\slash migration rate as a component of broader demographic history (\emph{e.g.}, Approximate Bayesian Computation (ABC) \cite{beaumont2002}, diffusion approximations for demographic inference ($\delta a\delta i$) \cite{gutenkunst2009}, isolation with migration models \cite{hey2004}, and methods utilizing the sequentially Markovian coalescent (\emph{e.g.}, PSMC) \cite{li2011}). 
Rather, we focus on three categories of methods that explicitly identify introgressed genomic segments based on the extent of differentiation, patterns of nucleotide/haplotype sharing, and phylogenetic relationships.

First, introgressed segments are expected to show low differentiation from their source population.
The $F_{st}$ and $d_{XY}$ statistics and derivates of $d_{XY}$ including $G_{min}$ \cite{geneva2015} and $RND_{min}$\cite{rosenzweig2016} gauge differentiation. 
The former two statistics are insensitive to rare migrants in a population and therefore lack power to detect very recent introgression, while the latter two overcome this limitation.
Additionally, $RND_{min}$ accounts for variable mutation rate, which is detected based on branch length to an outgroup \cite{rosenzweig2016}.
These statistics have been further developed by adding differentiation between both non-admixed ($A$) and admixed populations ($B$) and a source population ($C$) \cite{racimo2016}. 
For example, the $U_{A,B,C(w,x,y)}$ statistic summarizes the number of sites where an allele at frequency $y$ in the source population ($C$) has a frequency higher than $x$ in the admixed population ($B$) and lower than $w$ in the non-admixed population ($A$).
A similar statistic, $Q95_{A,B,C(w,y)}$, sets a hard cutoff at the $95^{th}$ percentile of allele frequency in the admixed population (B) \cite{racimo2016}.
Further modifications have allowed specification of more than one source population (see details in \cite{racimo2016}).
Since differentiation-based methods can be calculated site-by-site, high-density, genome-wide data are not necessarily required.
However, accuracy of introgression estimates is improved with more comprehensive data.
Phased data are also not a prerequisite for differentiation-based methods.

Second, ancestry deconvolution (also known as local-ancestry inference and chromosome painting) assigns genomic regions to various source populations based on patterns of allele or haplotype sharing \cite{schraiber2015}. 
One form of ancestry deconvolution utilizes a hidden Markov model to evaluate ancestry across admixed genomes through comparison to reference, non-admixed individuals (\emph{e.g.}, HAPMIX \cite{Price2009}). 
Another clusters admixed populations with reference samples using a sliding-window approach (\emph{e.g.}, PCAdmix \cite{brisbin2012pcadmix} and LAMP \cite{sankararaman2008}).
And, finally, a third version uses a Bayesian model \cite{pritchard2000} in which deviations from Hardy-Weinberg equilibrium are minimized through creation of genetic groups (\emph{e.g.}, fineSTRUCTURE \cite{Lawson2012}).
Ancestry deconvolution methods are better suited to high-density marker or whole genome sequencing data given the intent to assign ancestry genome-wide.
Many such methods also require accurate phasing of haplotypes.

Phylogenetic relationships are evaluated and applied to introgression detection using the ABBA-BABA statistic (also known as the D-statistic) and related metrics.
These statistics make inferences regarding introgression based on genomic patterns of derived variants that are shared between populations or species.
While the D-statistic is best suited to detection of introgression at the genome level, elaborations of the D-statistic including $\hat{f_{d}}$ \cite{martin2015} and $D_{\textrm{FOIL}}$ tests \cite{pease2015} are capable of localizing introgression to specific chromosomal regions. 
The former is quite similar to the D-statistic but uses allele frequencies from each population/species, and the latter can identify donor and recipient lineages of introgression in a more complex, five-taxon phylogeny.
Like differentiation methods, phylogeny-based detection of introgression can be employed using low-density data.
However, because these methods require knowledge of whether an allele is ancestral or derived, data from a sufficiently diverged outgroup must also be included in analyses.

Collectively, introgression detection methods have been applied across a wide range of systems, identifying several instances of adaptive introgression (see applications in \textbf{Table 1}).
For example, based on sequence divergence methods, introgression has been detected in \emph{Mimulus} (\emph{i.e.}, monkeyflower) species and appears to play a role in both adaptation to pollinator preference and speciation \cite{Stankowski2015}.
Likewise, the HAPMIX ancestry deconvolution method was applied by Jeong et al. \cite{jeong2014} to detect introgression in human populations from the Nepalese Sherpa to Tibetans at loci controlling high altitude adaptation.
Finally, the ABBA-BABA statistic has revealed introgression at wing coloration loci conferring M\"{u}llerian mimicry across butterfly species \cite{heliconius2012}.
Below we describe the nascent application of these methods to crop systems as well as implications for the study of domestication and adaptation.

As comprehensive genetic analyses of crops and their wild relatives have become feasible across their geographic ranges, evidence for substantial crop-wild introgression has been discovered in some of the world's most important crops (\textbf{Table 2}).
Below we present a summary of findings from maize, barley, rice, and potato, four systems in which crop-wild gene flow appears to have played an adaptive role.
All four of these crops were domesticated in defined centers and have subsequently expanded to much broader distributions, a migration that brought them into contact with new populations of wild relatives (Figure \ref{fig:map}).
For each case study below we describe what is known about both a crop's domestication history and the prevalence of adaptive introgression during post-domestication  expansion.

The relationship between maize (\emph{Zea mays} ssp. \emph{mays}) and the teosinte \emph{Zea mays} ssp. \emph{mexicana} (hereafter, \emph{mexicana}) offers a prime example of adaptive wild-to-crop introgression.
Maize was domesticated from \emph{Zea mays} ssp. \emph{parviglumis} (hereafter, \emph{parviglumis})  approximately 9,000 BP in the lowlands of the Balsas River Valley in Mexico \cite{matsuoka2002single}.
From this domestication center, maize spread into the highlands of the Mexican Central Plateau, where it came into sympatry with \emph{mexicana}.
Introgression from \emph{mexicana} to maize in the Central Plateau has been reported based on both morphological \cite {wilkes1977} and molecular \cite{vanHeerwaarden2011, doebley1987} data.
However, Hufford et al. \cite{Hufford2013} first localized \emph{mexicana} introgression to chromosomal regions and provided evidence that it was likely adaptive.
The authors identified nine genomic regions in several maize populations which consistently showed evidence of \emph{mexicana} introgression based on ancestry deconvolution methods including HAPMIX (Figure \ref{fig:introgressionMaize}).
These introgressed segments overlapped with QTL that had previously been found to control anthocyanin content and leaf macrohairs \cite{lauter2004}, traits known to be adaptive at high elevation.
In a growth chamber experiment, the authors demonstrated that maize populations with \emph{mexicana} introgression showed greater plant height (a proxy for fitness) under highland environmental conditions than populations that lacked introgression.
Height differences were not detected under lowland conditions, providing further evidence of local adaptation.

Populations of \emph{mexicana} cannot be found outside the highlands of Mexico, yet maize has colonized and adapted to high elevation in a number of other regions.
Wang and co-authors \cite{Wang2017} employed the ABBA-BABA and $\hat{f_{d}}$ statistics to evaluate if maize with \emph{mexicana} introgression was transferred to other highland regions or whether highland adaptation was obtained \emph{de novo} outside of Mexico.
Overall, analyses revealed that  \emph{mexicana} introgression was pervasive in maize from Mesoamerican high elevation regions (the highlands of Mexico, Guatemala, and the southwestern United States), but that more distant high elevation regions (\emph{e.g.,} the Andes) showed no \emph{mexicana} ancestry.
Maize from the lowlands of northern South America appears to have been derived from Mesoamerican lowland maize and high elevation adaptation in Andean maize likely occurred \emph{de novo} from this genetic base \cite{Takuno2015}.

\begin{figure}[h]
	\centering
	\includegraphics[width=12cm]{./FigsAndTables/Figure1new2}
	\caption{Evidence of adaptive introgression from \emph{mexicana} to Mexican highland maize on chromosome 4. A. Stacked bar plots of the HAPMIX introgression scan. Data adopted from Hufford et al. \cite{Hufford2013}. ELP: EL Porvenir; IXT: Ixtlan ; NAB: Nabogame; OPO: Opopeo; PUR: Puruandiro; SAC: Santa Clara; SAP: San Pedro; TEN: Tenango del Aire; XOC: Xochimilco. The dashed vertical lines indicate one of the QTLs for macrohairs and pigment density in Lauter et al. \cite{lauter2004}. B. Phenotypic differences between lowland (red) and highland (blue) maize stems. \label{fig:introgressionMaize}}.
\end{figure}

Barley (\emph{Hordeum vulgare} subsp. \emph{vulgare}) was likely domesticated multiple times from wild subsp. \emph{spontaneum} roughly 8,000 to 10,000 BP.
There is clear evidence of one domestication center in the Fertile Crescent \cite{badr2000origin, Morrell2007}, and others have supported additional eastern domestication events, potentially from subsp. \emph{spontaneum} east of the Zagros Mountains \cite{Morrell2007} or from subsp. \emph{spontaneum} var. \emph{agriocrithon} in modern-day Tibet \cite{dai2012tibet}.
However, recent research casts doubt on Tibetan domestication and suggests that var. \emph{agriocrithon} is not a wild relative, but rather a hybrid of domesticated landraces \cite{pourkheirandish2018elucidation}.
Presently, the distribution of wild barley stretches from the eastern Mediterranean through the Middle-East to west-central Asia, spanning clines in temperature, precipitation, soil type, and altitude \cite{Morrell2007}.
Cultivated barley is found throughout much of wild barley's distribution and crop-wild hybrids are fertile and common when these taxa co-occur.

Poets and co-authors \cite{Poets2015} recently investigated the range-wide contribution of wild barley to landraces, assessing both genome-wide and geographical patterns of introgression.
This study identified several lines of evidence consistent with wild introgression aiding the expansion and adaptation of domesticated barley.
The authors utilized ancestry deconvolution methods to identify genomic regions of shared ancestry, which linked particular landraces to numerous wild relative populations.
These results suggested landraces may have received wild introgression on a continual basis during post-domestication expansion.
However, barley landraces also showed an excess of ancestry from nearby wild relatives, indicating a prevalence of local and potentially adaptive gene flow.
Limited admixture linkage disequilibrium and small tracts of identity by state suggest substantial recombination has occurred since initial crop-wild hybridization and that even locally introgressed chromosomal regions are ancient, perhaps dating to the early expansion of barley post-domestication.
While these patterns suggest the possibility of adaptive introgression, wild barley haplotypes have yet to be definitively linked to specific adaptations in landraces post-domestication.

The details of Asian rice (\emph{Oryza sativa}) domestication are still debated.
Certain genetic and archaeobotanical evidence point toward independent domestications of the two prominent varietal groups \emph{japonica} and \emph{indica} from the wild species \emph{Oryza rufipogon} (\emph{rufipogon} hereafter) in China and the Indian Ganges plain, respectively \cite{fuller2010consilience}, with a potential third domestication event giving rise to the varietal group \emph{aus} in Bangladesh or central India \cite{civavn2015three}.
Other studies support a single domestication in China, with later divergence of \emph{japonica} and \emph{indica} \cite{molina2011molecular, Huang2012} during crop expansion.
For example, Huang and colleagues \cite{Huang2012} measured genetic distance between a range-wide sample of wild and domesticated rice, finding that \emph{japonica} was likely domesticated near the Pearl River in Guangxi province, China, and that \emph{indica} potentially resulted from hybridization between \emph{japonica} and local \emph{rufipogon} populations in southern and south-eastern Asia.
In a re-examination of these same data, Civ\'{a}\v{n} and colleagues \cite{civavn2015three} found evidence supporting independent domestications of \emph{japonica}, \emph{indica}, and \emph{aus}, as well as a hybrid origin (\emph{japonica} x \emph{aus}) of aromatic rice.
A recent third analysis by Choi and co-authors \cite{choi2018multiple} compared these two disparate results and the methods utilized therein, concluding that domestication alleles (including \emph{LABA1}, \emph{PROG1}, and \emph{sh1}) arose during a single domestication event of \emph{japonica}, and that these alleles introgressed into several wild \emph{rufipogon} subpopulations (crop-to-wild gene flow), which thereby became the progenitors of other Asian rice varieties.

The findings of \cite{choi2018multiple} bear similarities to a hypothesis posited by Vaughan and colleagues \cite{vaughan2008evolving} that also stresses the potential adaptive significance of crop-wild gene flow in rice.
According to this hypothesis, domestication alleles arose in a single cultivated rice population and subsequently introgressed into diverse cultivated populations (some \emph{japonica}-like, some \emph{indica}-like).
As these now fully domesticated populations spread further into new environments, they potentially received introgression from locally adapted wild relatives, retaining alleles that improved fitness.
While the precise history of domesticated rice remains in question, multiple lines of evidence indicate diverse wild populations have contributed to domesticated germplasm and suggest adaptive introgression may have played a role during the expansion of this important crop.

While potatoes are primarily propagated clonally, farmers do at times promote sexual reproduction for improvement of the crop and development of new cultivars \cite{quiros1992increase}.
Close proximity of domesticated potatoes and wild relatives, active hybridization, and local selection pressure favoring wild haplotypes across a diverse range of biotic and environmental conditions have likely fostered an expansion of genetic diversity within potatoes subsequent to domestication \cite{brush1995potato}.
The prevalence of wild introgression was recently clarified in a broad survey of potato diversity by Hardigan and colleagues \cite{hardigan2017genome}.
These authors discovered that, in particular, tetraploid domesticates had received extensive introgression from wild \emph{Solanum}, with a continued broadening of the genetic base of potato as it spread away from its Peruvian origin.
In certain cultivars, wild ancestry was estimated at upwards of 30\%.
Genes located within these introgressed regions were more likely to be highly-expressed and stress-inducible, and contained loci related to disease resistance, drought tolerance, and heat tolerance, suggesting introgression conferred adaptations critical to survival, possibly facilitating tolerance for new environmental pressures during range expansion \cite{hardigan2017genome}.
\end{enumerate}

The four crop systems described in detail here represent particularly compelling examples of wild introgression that was potentially adaptive.
However, given their similar histories, many additional crops have likely benefited from wild-to-crop gene flow during post-domestication expansion (\textbf{Table 1}).
Across these four cases studies, some generalities can be observed.
Data thus far indicate that wild introgression is often regional in its extent, but that, in certain cases (\emph{e.g.}, \emph{mexicana} haplotypes detected in maize landraces from the Guatemalan or southwestern U.S. highlands), newly introgressed wild haplotypes can be disseminated more broadly.
Additionally, when functional information is evaluated, as in the maize and potato studies, introgression has been found to occur at loci conferring adaptation to novel conditions not found in a crop's center of origin.
The possibility of both substantial and common wild gene flow raises a number of questions regarding both domestication and subsequent adaptation of crops.

\subsection*{What candidate genes were targeted by selection during domestication?}
Loci targeted by selection during domestication can be identified through so-called ``bottom-up'' approaches based on population genetic signatures \cite{Ross-Ibarra2007}.
Ideally, candidate loci will be identified by first constructing a demographic model representing the history of the domesticate.
In this approach, polymorphism data from neutral loci are fit to potential models of a crop's demography and then statistical tests of selection are used to identify candidate domestication genes under the most likely model.
Due to the uncertainty associated with any given demography, many studies identify domestication loci using a strict outlier approach in which loci showing, for example, the greatest reduction in nucleotide diversity or the highest allele frequency differentiation in the domesticate relative to the wild progenitor are identified as candidates.
Introgression during crop expansion may influence candidate gene detection using both demographic-modeling and strict-outlier approaches.
For example, \emph{mexicana} introgression into maize described above accounts for approximately 20\% of the genome of maize in the highlands of Mexico \cite{vanHeerwaarden2011}.
Takuno and co-authors \cite{Takuno2015} have shown that a demographic model incorporating this introgression is a significantly better fit to empirical data than a model lacking introgression.
Failure to account for introgression in maize would therefore compromise domestication candidate detection, particularly if a study contained maize samples from the Mexican highlands where \emph{mexicana} introgression is most prevalent.
Likewise, introgression that increased nucleotide diversity in the domesticate or decreased differentiation at domestication loci would confound a strict outlier approach.
However, previous work, also in maize, has shown that known domestication loci are particularly resistant to introgression \cite{Hufford2013}, likely due to ongoing selection favoring the domesticated phenotype.
\vspace{5mm}

While research in a subset of crops suggests adaptive wild introgression likely occurred, the scope and dynamics of this process are not yet fully described and remain unexplored in many systems.
In determining the extent and nature of adaptation due to introgression, several questions should be considered:

\subsection*{Do geographic patterns of introgression inform our understanding of adaptation?}
Conservation of the genomic architecture of introgression across individuals,  between populations, and across landscapes can help illuminate whether introgression is, in fact, adaptive.
For example, if an introgressed chromosomal region is conserved across a broad ecogeographic region, this suggests it may impart adaptation to more widespread environmental or climatic variables (\emph{e.g.}, cool temperatures at high elevation).
On the other hand, if genetic architectures of introgression are conserved across individuals within a population but not across populations in the region, this suggests much more local selective pressures (\emph{e.g.}, locally prevalent biotic pressures).
Highly variable introgression across individuals would be more consistent with random gene flow than adaptation.

\subsection*{From which wild taxa will introgression occur?}
As species become substantially diverged, introgression can become maladaptive or impossible due to Dobzhansky-Muller incompatibilities and other pre- and post-zygotic barriers.
Divergence time may therefore be a useful predictor of the possibility of gene flow between a particular wild relative and a domesticate.
Hybridization may also be limited between a crop and a particular wild relative due to genetic load. 
For instance, gene flow from a wild relative with a small long-term effective population size, and correspondingly high genetic load may not be favored by selection.
This effect has been observed in the case of Neanderthal introgression into humans, which was likely limited in extent and relegated largely to non-genic regions due to the high genetic load found within Neanderthal donor individuals \cite{harris2016genetic}.

Additional study of introgression in agroecosystems could lead to advances in crop improvement.
As described above, loci underlying the domesticated phenotype can be more clearly identified by removing the confounding population genetic signals of introgression.
These loci are potentially beneficial targets for crop improvement and their accurate identification is crucial.
Furthermore, adaptive introgression that is demonstrably tied to a specific environment represents a promising source of beneficial alleles that can be directly utilized in breeding to adapt crops to similar conditions.
Finally, as the historic role of wild relatives in the adaptation of crops is clarified, their conservation may be more prioritized, particularly as a resource for breeding in the face of future climate volatility and change.

Recent innovations in both high-density marker data and methods for characterizing genome-wide patterns of introgression have helped reveal the extent and timing of gene flow in a number of species.
Application of these data and techniques has led to mounting evidence of crop-wild gene flow following initial domestication in several crops.
Substantial post-domestication gene flow with wild relatives can affect inferences made regarding domestication and may be an important mechanism through which crops were able to adapt to novel conditions during global expansions.
An accurate understanding of the extent of gene flow is therefore important to both the basic study of crop evolution and to the identification of adaptive alleles for continued crop improvement.
While multiple studies in crop systems have identified wild introgression, fewer have effectively linked introgressed alleles to adaptation.
More comprehensive functional analyses and field evaluation will be critical for understanding the evolutionary and adaptive significance of introgression in crops.

Domesticated crops are among humanity's greatest inventions.
Interwoven in the genetic history of these crops is the story of our ancestors as they transitioned through the Agricultural Revolution.
In a more nuanced and dynamic understanding of crop domestication that includes sustained gene flow with wild relatives, we gain insight into the evolutionary journey that crops and humanity took, and continue to take, together.

\begin{adjustbox}{angle=90}
    %\begin{tabular}{llllll}
        \small
    \begin{tabular}{G{3cm}G{3.5cm}G{3cm}G{3.5cm}G{3.5cm}G{2cm}}
        \rowcolor{white}
    \\\toprule  
    {\bf Domesticated Crop}	& {\bf Compatible Wild Relatives } &	{\bf Hybrids and/or Hybridization} &  {\bf Evidence of Crop Introgression } &	{\bf Evidence of Adaptativeness} & {\bf Sources}\\ \midrule
    \rowcolor{gray!25}
Apple (\emph{Malus domesticus}) & \emph{M. sylvestris}, \emph{M. orientalis}, \emph{M. baccata}, \emph{M. sieversii}  & X & X & & \cite{ma2017reduced} \\
\rowcolor{white}
Asian Rice (\emph{Oryza sativa}) & \emph{O. rufipogon} & X & X & X & \cite{Huang2012} \\ 
\rowcolor{gray!25}
Barley (\emph{Hordeum vulgare}) & \emph{H. v.} subsp. \emph{spontaneum} & X & X & X & \cite{Poets2015} \\
\rowcolor{white}
Cassava (\emph{Manihot esculenta}) & \emph{M. glaziovii} & X & X & X & \cite{bredeson2016sequencing} \\
\rowcolor{gray!25}
Common Bean (\emph{Phaseolus vulgaris}) & \emph{P. v.} var. \emph{aborigineus, P. v.} var. \emph{mexicanus} [[not in this source]]& X & X &  & \cite{rendon2017genomic} \\
\rowcolor{white}
Grapes (\emph{Vitis vinifera} subsp. \emph{vinifera}) & \emph{V. v.} subsp. \emph{sylvestris} & X & X &  &  \cite{myles2011genetic} \\
\rowcolor{gray!25}
Maize (\emph{Zea mays} subsp. \emph{mays}) & \emph{Z. m.} subsp. \emph{mexicana}, \emph{Z. m. } subsp. \emph{parviglumis} & X & X & X & \cite{Hufford2013} \\
\rowcolor{white}
Olive (\emph{Olea europaea} ssp. \emph{europaea} var. \emph{sativa}) & \emph{O. e.} ssp. \emph{europaea} var. \emph{sylvestris} & X & X & & \cite{diez2015olive} \\ 
\rowcolor{gray!25}

Potato (\emph{Solanum tuberosum}) & many & X & X & X & \cite{hardigan2017genome}\\
\rowcolor{white}
Soybeans (\emph{Glycine max}) & \emph{G. soja} & X & X &  & \cite{han2016domestication} \\

\rowcolor{white}
 Wheat (\emph{Tritium monococcum, T. dicoccum, T. aestivum}) & \emph{T. m. boeoticum, T. dioccoides, T. urartu, Aegilops speltoides, A. tauschii} & X & X &  & \cite{dvorak2006molecular} \\
%luo2007structure would be another appropriate citation for wheat (it is cited by dvorak2006molecular.  Strange that a paper from 2006 can cite a paper from 2007...
    \end{tabular}
\end{adjustbox}

\end{document}
>>>>>>> 5130319157684b7bcffe4fe841969d5bc77b5a8d
